Accelerated oblique random survival forests

### 2022-06-21 docs/index.Rmd
including coxtime

---
title: "Accelerated oblique random survival forests"
author: "Byron C. Jaeger"
date: Last updated `r Sys.Date()`
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

Start with a multivariate normal draw

- All columns have a mean of zero and standard deviation of 1.

- Pairwise correlations are selected at random uniformly between a lower and upper boundary.

- A predictor matrix including interactions, non-linear mappings, and linear combinations is used to generate a time-to-event outcome using the `simsurv` R package

- Transforms are dropped from the matrix after generating the outcome values.

@@

VI techniques are compared based on their discrimination (C-statistic) between relevant and irrelevant variables.

Normally a C-statistic assesses if a predicted score discriminates between positive and negative cases of a binary outcome.

We use the C-statistic differently by treating each variable like a binary outcome (e.g., the outcome is 1 if the variable is relevant, 0 otherwise).

In other words, we assess VI as if it were a ‘prediction’ for the status of the variable. (can only do this for simulated data).

The resulting C-statistic measures the probability that a VI technique will rank a relevant variable higher than an irrelevant variable.

>>>>

---
title: "Accelerated oblique random survival forests"
author: "Byron C. Jaeger & Nicholas Pajewski"
date: Last updated `r Sys.Date()`
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

@@

We compute a C-statistic for each VI technique based on its discrimination between relevant and irrelevant variables.

- Treat each variable like a binary outcome

    + The outcome is 1 if the variable is relevant
    + The outcome is 0 if the variable is not relevant

- Treat VI as if it were a ‘prediction’ for the status of the variable.
